The Weakly Nonlinear Magnetorotational Instability

### 2016-09-02 paper/widegap_mri_paper.tex
search widegap critical parameters to flesh out satamp plot. Pm=4E-6

We examine the behavior of the wide gap MRI system as a function of $Pm$. Figure \ref{fig:coefficients} shows the critical parameters $k_c$ and $\reym$ as a function of $Pm$, as well as the coefficients $b$, $c$, and $d$. The GLE coefficients are remarkably insensitive to $Pm$. From Equation \ref{eq:gle} it is readily apparent that the asymptotic saturation amplitude is $\alpha_{s} = \pm \sqrt{b/c}$, so we conclude that the saturation amplitude of the MRI is only very weakly dependent on $Pm$. Note that because $\reym$ is essentially constant as a function of $Pm$, the saturation amplitude is equivalently insensitive to $\reye^{-1}$. This is in stark contrast to the narrow gap behavior of the system. For these same boundary conditions, \citeauthor{Umurhan:2007hs} (\citeyear{Umurhan:2007hs}) find that the narrow gap saturation amplitude scales as $Pm^{-4/3}$. They find that this amplitude dependence is driven by the $Pm^{1/3}$ dependence of the linear boundary layer. Boundary layer analysis similarly reveals a $\nu^{1/3}$ dependence for the radial extent of the boundary layer (\citei{Goodman:2002ix}). Why does the $Pm$ scaling of the boundary layer width not translate to a stronger $Pm$ scaling for the saturation amplitude in the wide gap case? The boundary layer in the wide gap case is strongly localized at the walls, i.e. $r_1$ and $r_2$. Figure \ref{fig:wide_narrow_N31B} shows the structure of the third-order nonlinear term $N_{31}^{(B)}$ as a function of $Pm$ for both the narrow and wide gap standard MRI. $N_{31}$ is the vector that determines the GLE coefficient $c$ (see Appendix \ref{app:basic_equations} for the wide gap case, and \citei{Umurhan:2007hs}, \citei{Clark:2016} for the narrow gap equations). Clearly, the boundary layers scale with $Pm$ in both the wide and narrow gap MRI. However, in the narrow gap case this scaling extends prominently into the center of the channel, whereas for the wide gap case the bulk of the flow is relatively unaffected by the boundary layer scaling.

>>>>

We examine the behavior of the wide gap MRI system as a function of $Pm$. Figure \ref{fig:coefficients} shows the critical parameters $k_c$ and $\reym$ as a function of $Pm$, as well as the coefficients $b$, $c$, and $d$. The GLE coefficients are remarkably insensitive to $Pm$. From Equation \ref{eq:gle} it is readily apparent that the asymptotic saturation amplitude is $\alpha_{s} = \pm \sqrt{b/c}$, so we conclude that the saturation amplitude of the MRI is only very weakly dependent on $Pm$. Note that because $\reym$ is essentially constant as a function of $Pm$, the saturation amplitude is equivalently insensitive to $\reye^{-1}$. This is in stark contrast to the narrow gap behavior of the system. For these same boundary conditions, \citeauthor{Umurhan:2007hs} (\citeyear{Umurhan:2007hs}) find that the narrow gap saturation amplitude scales as $Pm^{2/3}$. They find that this amplitude dependence is driven by the $Pm^{1/3}$ dependence of the linear boundary layer. Boundary layer analysis similarly reveals a $\nu^{1/3}$ dependence for the radial extent of the boundary layer in Taylor Couette flow (\citei{Goodman:2002ix}). Why does the $Pm$ scaling of the boundary layer width not translate to a stronger $Pm$ scaling for the saturation amplitude in the wide gap case? The boundary layer in the wide gap case is strongly localized at the walls, i.e. $r_1$ and $r_2$. Figure \ref{fig:wide_narrow_N31B} shows the structure of the third-order nonlinear term $N_{31}^{(B)}$ as a function of $Pm$ for both the narrow and wide gap standard MRI. $N_{31}$ is the vector that determines the GLE coefficient $c$ (see Appendix \ref{app:basic_equations} for the wide gap case, and \citei{Umurhan:2007hs}, \citei{Clark:2016} for the narrow gap equations). Clearly, the boundary layers scale with $Pm$ in both the wide and narrow gap MRI. However, in the narrow gap case this scaling extends prominently into the center of the channel, whereas for the wide gap case the bulk of the flow is relatively unaffected by the boundary layer scaling.
